---
title: "Week2HandIn"
author: "DominicGeard"
format: html
---

## Project 1

The following code shows which rows contain NA values

```{r}
df <- data.frame(airquality)
naRows <- which(apply(df,1,function(row) any(is.na(row))))

naRows 
```

The following Code shows the mean of Temperature and Ozone respectively.

```{r}
MeanTemp <-  mean(df$Temp, na.rm = TRUE)
MeanTemp
MeanOzone <- mean(df$Ozone, na.rm = TRUE)
MeanOzone
```

The following Code shows the standard deviation of Temperature and Ozone respectively.

```{r}
sdTemp <- sd(df$Temp, na.rm = TRUE)
sdOzone <- sd(df$Ozone, na.rm = TRUE)
sdTemp
sdOzone
```

The following Code shows the maximum of Temperature and Ozone respectively.

```{r}
maxTemp <- max(df$Temp, na.rm = TRUE)
maxOzone <- max(df$Ozone, na.rm = TRUE)
maxTemp
maxOzone
```

The following Code shows the minimum of Temperature and Ozone respectively.

```{r}
minTemp <- min(df$Temp, na.rm = TRUE)
minOzone <- min(df$Ozone, na.rm = TRUE)
minTemp
minOzone
```

Finding the estimate for the cars data set fitted to a linear regression model.

```{r}
Y <- as.matrix(cars$dist)
X <- cbind(1, cars$speed)
est <- solve(t(X)%*%X)%*%t(X)%*%Y
est
```

The linear regression model summary:

```{r}
fit <- lm(cars$dist~cars$speed)
summary(fit) 
```
